Millions of Type Errors

### 2023-03-10 oopsla23/paper.tex
roblox context notes
plot telemetry records per hour for the sample dataset

\usepackage{alltt}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

@@

\section{Predictions}

@@

>>>>

\usepackage{alltt}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\paragraph{Creating Experiences}

more than games

telemetry gets a session id per experience

@@

\section{Telemetry Design}

No PII whatsoever

Random session selection

Random events during session, except module switch.

No access to other key events: save, exit.
Don't want access to run, publish.

\url{https://docs.google.com/document/d/1DnKvw8x1jy0EWCbBSM8neKULWz7WAg1OauKy7qqYqkI/edit}

\section{Predictions}
%%bg: merge with prev section, on telemetry design?

@@

\begin{figure}[t]
  \includegraphics{img/row-distribution.pdf}
  \Description{TBD: histogram with about 100 records per hour except for a 600-record spike near the end of Jan 12th.}
  \caption{Telemetry records per hour. Each tick on the $x$-axis marks the start of a new day in California.}
  \label{f:records-per-hour}
\end{figure}

\Cref{f:records-per-hour} shows when data arrived across the whole dataset.
